Follow-up Samples

### 2017-09-13 submission/manuscript_R2.Rmd
add importance statement and R2 to makefile

>>>>

## Importance

This study helps to clarify what happens to the microbiota after generalized treatment for an adenoma or carcinoma. It is a necessary first step to ultimately investigating how the microbiota changes in those with carcinoma recurrence. This is important since a large number of those treated for carcinoma will have a recurrence. Finding better ways to stratify those most and least likely to recur using the microbiota could provide a cheaper and more accurate alternative to the current status quo. Our results suggest that the microbiota could be used to stratify individuals for risk of recurrence and provides a starting point for future studies into this area.

### 2017-09-13 submission/manuscript_R2.tex
add importance statement and R2 to makefile

>>>>

\subsection{Importance}\label{importance}

This study helps to clarify what happens to the microbiota after
generalized treatment for an adenoma or carcinoma. It is a necessary
first step to ultimately investigating how the microbiota changes in
those with carcinoma recurrence. This is important since a large number
of those treated for carcinoma will have a recurrence. Finding better
ways to stratify those most and least likely to recur using the
microbiota could provide a cheaper and more accurate alternative to the
current status quo. Our results suggest that the microbiota could be
used to stratify individuals for risk of recurrence and provides a
starting point for future studies into this area.
